Supplement 2

### 2020-10-30 paper/supplement-2.Rmd

```{r libraries, message = FALSE}
library(tidyverse)
library(kableExtra)
library(knitr)
library(conflicted)
library(gt)
library(PRISMAstatement)
library(DiagrammeRsvg)
conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")
```

@@

```{r read-gs-data}

>>>>

@@

```{r loadd-targets}
loadd(gs_football)
loadd(gs_mismatches)
loadd(simulated_afl_data)
loadd(gs_football_final_matches)
```
